Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-08 analysis/paper/paper.Rmd
Add metadata & title to Figure 3 as suggested by Reviewer 1

    node [shape = box, style = filled, fillcolor = grey99, width = 1.2,fontname = Helvetica]
    Question; Methodology; Data; Analysis; Manuscript;

    node [shape = box, style = filled, fillcolor = grey90, width = 1.2,fontname = Helvetica]
    Description; Availability; Citation

>>>>

    node[shape = plaintext, width = 1.2, fontname = Helvetica, fontsize = 20]
    'An open and reproducible workflow'

    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
    Question; Methodology; Data; Analysis; Manuscript;

    node [shape = box, style = filled, fillcolor = grey90, width = 1.2, fontname = Helvetica]
    Description; Availability; Citation
